---
title: "Jeff's Analysis, 5/15"
output:
  html_document:
  theme: united
---

Alright here is some start up to load the Bayes factors.
```{r,message=FALSE,warning=FALSE}
library('BayesFactor')
if (!file.exists('bf.RData')) source('doBf.R')

load('bf.RData')
ans8=bf[[1]]
ans9=bf[[2]]
ansDif=bf[[3]]
```

# frac8 for eigth graders

Let's look at the top 20 models
```{r}
head(ans8,20)/head(ans8)[1]
```

The best model is *IQ1 + WNL1 + frac_cpt7 + math7*, which is only slightly better (1-to-.94) than *IQ1 + frac_cpt7 + math7*, the best 3-covariate model.  The difference shows that *WLN1* is not strictly needed if *IQ1* is included.  The two other plausible three-covariate competitors are *WNL1 + frac_cpt7 + math7* and *frac_cpt7 + math7 + ef5*, which are 1-to-.65 and 1-to-.47 within the best model. These last two fits show that *IQ1* is not strictly needed as well and may be replaced with *WLN1* or even *ef5*. 

Here is grist for the table:

Best 4:   
IQ1 + WNL1 + frac_cpt7 + math7                    : 1   

Best 3:  
IQ1 + frac_cpt7 + math7                           : 0.941645  
WNL1 + frac_cpt7 + math7                          : 0.6527834  
frac_cpt7 + math7 + ef5                           : 0.4709651  

The common factors are *frac_cpt7* and *math7*.  Are they necessary?

```{r}
best3=(names(ans8@numerator)=="IQ1 + frac_cpt7 + math7")
b3wofrac_cpt7=(names(ans8@numerator)=="IQ1 + math7")
b3womath7=(names(ans8@numerator)=="IQ1 + frac_cpt7")
ans8[best3]/ans8[b3wofrac_cpt7]
ans8[best3]/ans8[b3womath7]
```

Are they sufficient?
```{r}
myTwo=(names(ans8@numerator)=="frac_cpt7 + math7")
ans8[best3]/ans8[myTwo]
```

# Ignore After Here



top9=head(ans9,35) 
topDif=head(ansDif,4) 
prior9 = newPriorOdds(top9, type = "equal")
post9 = prior9 * top9
post.prob9 = as.BFprobability(post9)

extractBF(top9/top9[1])[,1:2]             

#best 5
IQ1 + WNL6 + frac_add7 + frac_cpt7 + ef1                  1.0000000 0.000000e+00
IQ1 + WNL6 + frac_cpt7 + ef5 + numset1                    0.8912493 4.900876e-08
IQ1 + WNL6 + frac_add7 + frac_cpt7 + ef5                  0.7964367 4.780000e-08
IQ1 + WNL1 + WNL6 + frac_cpt7 + math7                     0.6637877 4.604925e-08
WNL1 + WNL6 + frac_cpt7 + math7 + ef5                     0.6028195 4.521898e-08
WNL6 + frac_cpt7 + math7 + ef5 + numset1                  0.5716441 4.478772e-08
IQ1 + WNL6 + frac_cpt7 + math7 + numset1                  0.4920271 4.366432e-08
---------------------------



#best 4
WNL6 + frac_cpt7 + ef5 + numset1                          0.4648663 2.938088e-05
IQ1 + WNL6 + frac_cpt7 + numset1                          0.3909489 2.961897e-05
WNL1 + WNL6 + frac_cpt7 + math7                           0.3901336 2.962251e-05


OK, so it seems that frac_cpt7 and WNL6 are needed.  Yi, how bad is the best 5 and the best 4 minus each of these?

frac_cpt7

best5=(names(ans9@numerator)=="IQ1 + WNL6 + frac_add7 + frac_cpt7 + ef1")
best4=(names(ans9@numerator)=="WNL6 + frac_cpt7 + ef5 + numset1")

b5wWNL6=(names(ans9@numerator)=="IQ1 + frac_add7 + frac_cpt7 + ef1")
b5wfrac_cpt7=(names(ans9@numerator)=="IQ1 + WNL6 + frac_add7 + ef1")
b4wWNL6=(names(ans9@numerator)=="frac_cpt7 + ef5 + numset1")
b4wfrac_cpt7=(names(ans9@numerator)=="WNL6 + ef5 + numset1")

#we have a great story!
ans9[b5wWNL6]/ans9[best5]
ans9[b4wWNL6]/ans9[best4]
ans9[b5wfrac_cpt7]/ans9[best5]
ans9[b4wfrac_cpt7]/ans9[best4]

top2=(names(ans9@numerator)=="WNL6 + frac_cpt7")
ans9[top2]/ans9[best5]

--------------------------
Improvements for Richard---
a. add numbers of covariates
b. add prior odds weight by covariates
c. add averaging by covariate (dont ave models less than x from top)
